\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-30 NAR_DRAFT.tex
ick, but moving in the right direction

In practice, accurate calibration is most important for variants with high posterior probability.
For variants with posterior probability between 60 and 90\%, \batcave is substantially better calibrated than MuTect (Fig.~\ref{NAR-ppv_fig}\&\ref{NAR-ppv_wgs_fig}).
For any posterior probability above 70\%, MuTect has a false positive rate of roughly 8\%, whereas \batcave has a false positive rate that decreases as the posterior probability increases.
The cost of MuTect's compression is recall, which is 3-5\% worse than \batcave at 95\% posterior probability, and 3-7\% worse at 90\%, depending on mutation profile concentration.
At any posterior probability \batcave returns a larger fraction of all positive calls than MuTect. \rngcomment{What does this mean?}
%Figure~\ref{NAR-ppv_wgs_fig} shows results for 100X whole genomes, where the results are similar for precision.

>>>>

In practice, variant calling is a decision problem, in which a threshold must be selected above which we accept a variant call.
The proper threshold is ideally a choice the user makes based on their particular needs.
For variants with posterior probability between 60 and 90\%, \batcave is substantially better calibrated than MuTect (Fig.~\ref{NAR-ppv_fig}\&\ref{NAR-ppv_wgs_fig}).
For any posterior probability above 70\%, MuTect has a false positive rate of roughly 8\%, whereas \batcave has a false positive rate that decreases as the posterior probability increases.
The cost of MuTect's compression is recall, which is 3-5\% worse than \batcave at 95\% posterior probability, and 3-7\% worse at 90\%, depending on mutation profile concentration.
At any posterior probability \batcave returns a larger fraction of all positive calls than MuTect. \rngcomment{What does this mean?}
%Figure~\ref{NAR-ppv_wgs_fig} shows results for 100X whole genomes, where the results are similar for precision.
